User Privacy in the Public Bitcoin Blockchain

### 2014-07-29 paper.tex
added acks

\author{Name~Surname, %~\IEEEmembership{Member,~IEEE,}
        Name~Surname, %~\IEEEmembership{Fellow,~OSA,}
        Name~Surname, \IEEEmembership{Member, IEEE,}
        Name~Surname, %~\IEEEmembership{Fellow,~OSA,}
        and~Name~Surname,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
\thanks{The authors %are with Universitat Pompeu Fabra.
%Roc Boronat 138, 08018 Barcelona, Catalunya, Spain.
%E-mail: jaume.barcelo@upf.edu
%This paper has been submitted to an IEEE journal.
}
}

@@

The authors would like to thank ...

>>>>

\author{Jaume~Barcelo% <-this % stops a space
\thanks{The author is with Universitat Pompeu Fabra.
Roc Boronat 138, 08018 Barcelona, Catalunya, Spain.
E-mail: jaume.barcelo@upf.edu
}
}

@@

The author would like to thank Amir Taaki and the other developers of libbitcoin and obelisk for providing the code used to gather the statistics.
